An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-27 paper.tex
Update Section 2.3 (Ethics)

The data we analyse is extracted from public IETF archives and APIs.  We
have taken steps to ensure ethical compliance.  To ensure that our access
to these services does not cause operational problems for the IETF, we are
in regular contact with the IETF Tools Team and Secretariat, as well as the
operators of the Datatracker and mailing list archive.  We have extensively
discussed our work with IETF leadership (IETF and IAB Chairs, the IETF
Executive Director, and the IRTF Chair, who is a co-author on this paper)
and the RFC Editor to ensure that our access falls within their acceptable
use policies.

Participation in the IETF is dependent on agreement to abide by the
policies and procedures described at \url{https://www.ietf.org/about/note-well},
including the privacy policy at \url{https://www.ietf.org/privacy-statement}.
These make explicit provision that mailing list archives and the metadata
contained in the Datatracker system will be made public, and it is this
public data that we process to extract the aggregate statistics presented
in Sections \ref{sec:documents}, \ref{sec:authors}, and \ref{sec:mail}, as
well as the features analysed in Section \ref{sec:model}. We transfer and
store data securely, and retain it only for the time needed to perform the
analysis.  Since we operate entirely using the public APIs provided by
IETF, we have no access to private data about individuals.

@@

%==================================================================================================
\section{Trends in Participant Demographics}

@@

%==================================================================================================
\section{Understanding Participant Behaviour}

@@

%==================================================================================================
\section{Success Factors}

>>>>

% The following is adapted from our IMC 2021 paper:

The data we analyse is extracted from public IETF archives and APIs.  We
have taken steps to ensure ethical compliance.  To ensure that our access
to these services does not cause operational problems for the IETF, we are
in regular contact with the IETF Tools Team and Secretariat, as well as the
operators of the Datatracker and mailing list archive.  We have
discussed our work with IETF leadership (IETF and IAB Chairs, the IETF
Executive Director, and the IRTF Chair, who is a co-author on this paper)
and the RFC Editor to ensure that our access falls within their acceptable
use policies.

Participants in the IETF must agree to abide by the policies and procedures
described at \url{https://www.ietf.org/about/note-well}, including the privacy
policy at \url{https://www.ietf.org/privacy-statement}. These make explicit
provision that mailing list archives and the metadata contained in the
Datatracker system will be made public, and it is this public data that
we process to extract the aggregate statistics presented in Sections
\ref{sec:trends-documents}, \ref{sec:trends-demographics}, \ref{sec:org-dynamics},
\ref{sec:behaviour} as well as the features analysed in Section
\ref{sec:success-factors}. We transfer and store data securely, and retain
it only for the time needed to perform the analysis.  Since we operate
entirely using the public APIs provided by IETF, we have no access to
private data about individuals.

@@

%==================================================================================================
\section{Trends in Participant Demographics}
\label{sec:trends-demographics}

@@

%==================================================================================================
\section{Understanding Participant Behaviour}
\label{sec:behaviour}

@@

%==================================================================================================
\section{Success Factors}
\label{sec:success-factors}
